### 2018-06-29 doc/plos/text/manuscript.tex
add contribution subsection

@@

TODO~\cite{farrow2016modeling}

@@

>>>>

\subsection*{Contribution}

We propose nowcasting influenza through \emph{sensor
fusion}~\cite{farrow2016modeling} of digital surveillance. Derived from the
Kalman filter \cite{kalman1960new}, sensor fusion is optimal in a least-squares
sense (up to assumptions of independence and normality), robust to noise,
tolerant of missing data, and capable of assimilating data across varying
geospatial resolutions. We implement a sensor fusion framework and apply it to
nowcasting ILI in US states and territories (and in any combination thereof,
including HHS regions, census divisions, and the US as a whole), based on the
assimilation of any and all surveillance data available at runtime.

@@

@@

\bibitem{kalman1960new}
Kalman RE.
\newblock A new approach to linear filtering and prediction problems.
\newblock Journal of basic Engineering. 1960;82(1):35--45.
